% RYUON Reference Manual
% Copyright (C) 2007-2008 Kengo Ichiki <kichiki@users.sourceforge.net>
% $Id: reference.tex,v 1.1 2008/07/11 04:18:35 kichiki Exp $

%\documentclass{book}
\documentclass[twocolumn]{book}

\usepackage[dvips]{graphicx}
\usepackage{amsmath}
% some trick to prevent "Too many math alphabets" error for "bm" package
\newcommand\bmmax{0}
\usepackage{bm}
\usepackage{times}
\usepackage{txfonts}
\usepackage{mathrsfs}

\begin{document}

\title{RYUON Reference Manual}
\author{Kengo Ichiki
 \thanks{e-mail: kichiki@users.sourceforge.net}}
\date{\today}

\maketitle

\tableofcontents

\chapter{Introduction}
This document describes details of some numerical implementations 
of {\bf RYUON} (aiming for developers).


There are other documents:
\begin{itemize}
\item ``RYUON User's Manual'':
  describing overview and some tutorials of {\bf RYUON} (for users).
\item ``RYUON Reference Manual'':
  describing numerical implementations 
  of {\bf RYUON} (for developers).
\item ``Theory of RYUON'':
  a textbook describing theoretical background of {\bf RYUON}
  (for researchers).
\end{itemize}


\chapter{General Mobility Problem -- ${\bf A}\cdot\bm{x}$ Calculation}
\label{chp:atimes}


\chapter{Mobility Problem}
\label{chp:mob}


\chapter{Resistance Problem}
\label{chp:res}


\chapter{Mixed Problem}
\label{chp:mix}


\chapter{Lubrication}
\label{chp:lub}

\section{Top Layer}
The lubrication forces for $N$ (all) particles 
The lubrication forces for $N$ (all) particles 
\begin{equation}
  \bm{F}
  =
  \bm{L}
  \cdot
  \bm{U}
  ,
\end{equation}
is calculated by
\begin{equation}
  {\tt calc\_lub\_\langle d\rangle\langle ver\rangle\ (sys, u, f)}
  ,
\end{equation}
which is called by the top-level function
\begin{equation}
  {\tt solve\_\langle type\rangle\_lub\_\langle d\rangle\langle ver\rangle\ ()}
  ,
\end{equation}
for mobility, resistance, and mixed problems ({\tt type}) 
in 2- and 3-dimensions ({\tt d}) 
with F, FT, and FTS versions ({\tt ver}).

The function ${\tt calc\_lub\_\langle d\rangle\langle ver\rangle\ ()}$ 
has particle-loops.
Under the periodic boundary condition, particles in the image cells 
are also taken into account.

In the loop for particle-particle pairs, 
either 
\begin{equation}
  {\tt calc\_lub\_\langle ver\rangle\_2b()}
\end{equation}
for monodisperse system or
\begin{equation}
  {\tt calc\_lub\_\langle ver\rangle\_2b\_poly()}
\end{equation}
for polydisperse system is called.


\section{Polydisperse Systems}
All information necessary to calculate the interactions for 
polydisperse systems are stored in the struct {\tt twobody\_f} 
for each pair characterized by the size ratio 
$\lambda := a_2 / a_1$. 

\begin{itemize}
\item {\tt calc\_lub\_[f,ft,fts]\_2b\_poly()} in f.c, ft.c, fts.c:\\
  calculate lubrication forces (and torques and stresslets) by 
  \begin{equation}
    \left[
      \begin{array}{c}
        \bm{F}^{(1)} \\ \bm{F}^{(2)}
      \end{array}
    \right]
    =
    \bm{L}_{\text{2B}}
    \cdot
    \left[
      \begin{array}{c}
        \bm{U}^{(1)} \\ \bm{U}^{(2)}
      \end{array}
    \right]
    ,
  \end{equation}
  for particles {\tt i1} and {\tt i2}
  at {\tt x1[3]} and  {\tt x2[3]}, respectively.
  This calculation is done in the SD scaling, 
  achieved by the function 
  {\tt scalars\_res\_poly\_scale\_SD()}.
  The function 
  {\tt scalars\_lub\_poly\_full()} is called 
  to obtain the scalar functions of the lubrication matrix.
\item {\tt scalars\_lub\_poly\_full()} in minv-poly.c:\\
  calculate scalar functions of lubrication matrix defined by 
  \begin{equation}
    \bm{L}_{\text{2B}}
    :=
    \bm{R}^{\text{exact}}_{\text{2B}}
    -
    \left(
      \bm{M}^{\infty}_{\text{2B}}
    \right)^{-1}
    .
  \end{equation}
  In this routine, the functions 
  {\tt twobody\_scalars\_res()} and 
  {\tt scalars\_minv\_[f,ft,fts]\_poly()} are called.
  The former is called twice to obtain scalar functions 
  for $12$- and $21$-pairs in $\bm{R}^{\text{exact}}_{\text{2B}}$, 
  and the latter is once for $(\bm{M}^{\infty}_{\text{2B}})^{-1}$.
  The scalar functions are in the dimensional form.
\item {\tt twobody\_scalars\_res()} in twobody.c:\\
  This routine handles whether lubrication form is used 
  for the exact solution (to improve the convergence), and 
  the scaling of the result scalar functions.
\end{itemize}


\chapter{Periodic Boundary Condition}
\label{chp:ewald}



\chapter{Brownian Dynamics}



\chapter{Connections and Bond Interactions}
\label{chp:bonds}

\input{ref-bonds-groups.tex}



%\bibliographystyle{abbrv}
%\bibliographystyle{alpha}
%\bibliographystyle{apalike}
%\bibliographystyle{ieeetr}
%\bibliographystyle{plain}
\bibliographystyle{siam}
%\bibliographystyle{unsrt}
%\bibliographystyle{prsty}
\bibliography{mine,stokes,fmm,opensource}

\end{document}
